### 2020-01-30 ChapterResults/chapterResults.tex
Updated: Language corrections in Results

\subsection{Collision Error Detection}
It is possible to detect late collisions between objects; Given the relative speed of the two objects and the physics time-step, it possible to calculate the maximum expected penetration distance. If a collision is detected and it is above this value, it means it is a late collision. In addition, if no collisions occurs, it means there is a missed collision.

@@

Using the above method to detect late collisions, we will now perform experiments on a distributed configuration of a simulation. Experiments were carried out for both variations in all three aura tolerance factors and packet-loss. Experiments were conducted using AWS G2.2xlarge servers located within the same geographical region. A G2.2xlarge instance uses a 2.60GHz Intel Xeon E5-2670 CPU with 16GB RAM and an NVIDIA GRID K520 (Kepler) GPU running Ubuntu 18.04 LTS.

\subsection{Varying Factors}
Experiments were carried out to demonstrate the effects of varying each aura calculation factor on the correctness of collisions between objects. The purpose of these experiments is to demonstrate that collisions in AP are always correct, i.e. there are no late or missed collisions, if the three factors that determine aura size remain within respective tolerances and correctness is no longer guaranteed if the tolerances are exceeded. In addition, if the aura calculation is correct, we expect to see late collisions begin to occur as soon as tolerances are exceeded. If errors do not occur as soon as the tolerances are exceeded, this is evidence that the aura radius is too large. Large auras can lead to reduced performance in AP, therefore auras that are only as large as needed to be, for the given tolerance, are desirable to maximise performance.

@@

Speed is controlled such that the two objects used in the experiment collide with each other with that desired speed. Latency is controlled using the Traffic Control tool to emulate latency for all communications between the servers. The desired latency is applied as a fixed delay to each server, resulting in that delay being applied to all packets outgoing from that server. Frame-time is controlled using a wait within the simulation's update loop, this is limited to a target frame-time as the resultant frame-times are a normal distribution with the target frame-time as the median. This is illustrated in Fig. \ref{fig_FrameTimeDensity}. As a result of this, half of all frames are expected to be above the target frame-time, which may cause false-positives in detecting late collisions, in the following experiments. However, the variance in frame-time is low, longer frames have to occur exactly at the time of messages being exchanged, and due to the fact that factors can compensate for other factors, false-positives are expected to be rare up until the tolerance value is approached. It should be noted that variance increases with target frame-time, therefore more false-positives should expected with experiments using higher target frame-times.

@@

\subsubsection{Evaluation}
As the speed increases, the mean penetration time increases, with the exception of 0 speed, the standard deviation remains constant, below the tolerance line, once above the tolerance line, the stand deviation increases relative to below the tolerance line, but appears to remain constant. Note that the mean error increases in discrete steps (with some small variation), this is due to the discrete physics time-steps. Object speed is application specific and objects needs to to be travelling directly towards the centre of each other and one of the objects has to be travelling above the tolerance speed, in order for errors to occur.

@@

\subsubsection{Experiment parameters and output}
The two servers use the following tolerances: a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$; maximum latency tolerance of $2ms$; and a maximum frame-time tolerance of $15ms$. Each server has a random delay before starting between $0$ and the target frame-time in order to prevent the two servers always having synchronous update cycles. Each experiment is repeated $50$ times. The mean and $+/-2$ standard deviations of penetration time were plotted against each tolerance factor for each of the three tolerance values chosen. In addition, the ratio of errors to correct Collisions and misses to total collisions were plotted against packet-loss.

>>>>

\subsection{Collision Error Detection}
It is possible to detect late collisions between objects; Given the relative speed of the two objects and the physics time-step, it possible to calculate the maximum expected penetration distance. If a collision is detected and it is above this value, it means it is a late collision. In addition, if no collisions occur, it means there is a missed collision.

@@

Using the above method to detect late collisions, experiments on a distributed configuration of a simulation will now be performed. Experiments were carried out for both variations in all three aura tolerance factors and packet-loss. Experiments were conducted using AWS G2.2xlarge servers located within the same geographical region. A G2.2xlarge instance uses a 2.60GHz Intel Xeon E5-2670 CPU with 16GB RAM and an NVIDIA GRID K520 (Kepler) GPU running Ubuntu 18.04 LTS.

\subsection{Varying Factors}
Experiments were carried out to demonstrate the effects of varying each aura calculation factor on the correctness of collisions between objects. The purpose of these experiments is to demonstrate that collisions in AP are always correct if the three factors that determine aura size remain within respective tolerance, i.e. there are no late or missed collisions. In addition, if the aura calculation is correct, we expect to see late collisions begin to occur as soon as tolerances are exceeded. If errors do not occur as soon as the tolerances are exceeded, this is evidence that the aura radius is too large. Large auras can lead to reduced performance in AP, therefore auras that are only as large as needed to be, for the given tolerance, are desirable to maximise performance.

@@

Speed is controlled such that the two objects used in the experiment collide with each other with that desired speed. Latency is controlled using the Traffic Control tool to emulate latency for all communications between the servers. The desired latency is applied as a fixed delay to each server, resulting in that delay being applied to all packets outgoing from that server. Frame-time is controlled using a wait within the simulation's update loop, this is limited to a target frame-time as the resultant frame-times are a normal distribution with the target frame-time as the median. This is illustrated in Fig. \ref{fig_FrameTimeDensity}. As a result of this, half of all frames are expected to be above the target frame-time, which may cause false-positives in detecting late collisions, in the following experiments. However, the following points should be considered: the variance in frame-time is low; longer frames have to occur exactly at the time of messages being exchanged; exceeding one factor can be compensated for by having a low value in another factor. Therefore, false-positives are expected to be rare up until the tolerance value is approached. It should be noted that variance increases with target frame-time, therefore more false-positives should expected with experiments using higher target frame-times.

@@

\subsubsection{Evaluation}
As the speed increases, the mean penetration time increases. With the exception of the starting speed, the standard deviation remains constant below the tolerance line. Once speed increases above the tolerance line, the standard deviation initially increases, but appears to remain constant after the initial increase. Note that the mean error increases in discrete steps (with some small variation), this is due to the discrete physics time-steps. Object speed is application specific and objects need to be travelling directly towards the centre of each other and one of the objects has to be travelling above the tolerance speed, in order for errors to occur.

@@

\subsubsection{Experiment parameters and output}
The two servers use the following tolerances: a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$; maximum latency tolerance of $2ms$; and a maximum frame-time tolerance of $15ms$. Each server has a random delay before starting between $0$ and the target frame-time in order to prevent the two servers always having synchronous update cycles. Each experiment is repeated $50$ times. The mean and $+/-2$ standard deviations of penetration time were plotted against each tolerance factor for each of the three tolerance values chosen. In addition, the ratio of errors to correct collisions and misses to total collisions were plotted against packet-loss.
